The Shape Matching Element Method for Meshless Animation of NURBs Models

### 2021-01-23 paper/sections/results.tex
performance table
add CPU column to table
blah

%
\section{Results}

\dave{we should show the nurbs model in rhino/fusion for every example, maybe an exploded view as well}

\dave{use as many different meshes as possible for figures (i.e try not to have the same mesh show up in more than one figure if possible).}

>>>>

%
\section{Results and Discussion}

\dave{we should show the nurbs model in rhino/fusion for every example, maybe an exploded view as well}
\dave{mention that not so many standard NURBS models so we modelled lots of these ourselves .. show's power of approach that we can model and sim all these examples.}
\dave{use as many different meshes as possible for figures (i.e try not to have the same mesh show up in more than one figure if possible).}

\begin{table*}[h]
  \caption{Performance of the Shape Matching Element Method on all Examples.}
  \label{tbl:compare}
  \begin{center}
  \begin{tabular}{l c c c c c c c c}
   \textbf{Example} & \textbf{CPU} & $|\vc{q}|$ &  \textbf{Sample Model} & \textbf{Quadrature} & \textbf{Weights} & \textbf{Build $\Pi$} & \textbf{Time Step} \\
   \hline 
   \rowcolor[HTML]{DAE8FC} 
   \textbf{Cantilever}  & ? & ? & ? & ? & ? & ? & ? & ? \\
   \textbf{Rocket}      & ? & ? & ? & ? & ? & ? & ? & ? \\
   \hline
  \end{tabular}
  \end{center}

  \end{table*}
